Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-12-02 leadership_across_cultures_contexts.Rmd
Minor MS changes here and bib edits.

NEED CONCLUSION PARAGRAPH/STATEMENT.

@@

NEED CONCLUSTION STATEMENT/PARAGRAPH.

@@

In sum, we seek to empirically and systematically accomplish the following four goals: 1) identify the most cross-culturally frequent *qualities of leaders* and the *functions they serve*. 2) Identify *features* of the qualities and functions of leaders (e.g., do particular variables tended to covary or cluster together?) in reference to theoretical models or novel interpretations. Such features might lend support to existing theories; for instance they might correspond to "prestige" and "dominance" [@henrich_evolution_2001]. 3) Identify the most cross-culturally frequent *costs and benefits* of leadership for both leaders and followers. Such exploratory results stand to facilitate more fine-grained approaches within leadership studies and greater theoretical and empirical work beyond community leadership, while also revealing the importance of a broad, cross-cultural perspective in understanding the psychology and cultural patterning of perhaps the most foundational component of human social behavior and organization.

>>>>

<!-- NEED CONCLUSION PARAGRAPH/STATEMENT.  -->

@@

<!-- NEED CONCLUSTION STATEMENT/PARAGRAPH.  -->

@@

In sum, we seek to empirically and systematically accomplish the following four goals: 1) identify the most cross-culturally frequent *qualities of leaders* and the *functions they serve*. 2) Identify *features* of the qualities and functions of leaders (e.g., do particular variables tended to covary or cluster together?) in reference to theoretical models or novel interpretations. Such features might lend support to existing theories; for instance they might correspond to qualities associated with "prestige" or "dominance" [@henrich_evolution_2001] or functions associated with conflict or cooperation [@gavrilets_collective_2015; @glowacki_evolutionary_2017; @hooper_theory_2010]. 3) Identify the most cross-culturally frequent *costs and benefits* of leadership for both leaders and followers. Such exploratory results stand to facilitate more fine-grained approaches within leadership studies and greater theoretical and empirical work beyond community leadership, while also revealing the importance of a broad, cross-cultural perspective in understanding the psychology and cultural patterning of perhaps the most foundational component of human social behavior and organization.
